SoK: The Evolution of Defenses Against Web Application Attacks

### 2014-11-04 docs/questioning.tex
more work on the analysis section / ease of use

There are also authors that took a different approach.
For instance, during their initial tests,
Stock et al.~\cite{SLMS14} managed to bypass
the browser-based {\sc xss} filters of the
73\% of 1,602 real-world {\sc dom}-based {\sc xss} vulnerabilities.
These vulnerabilities were actually found during
their previous research~\cite{LSJ13}.

>>>>

There are also authors that took a different approach.
For instance, during their initial tests,
Stock et al.~\cite{SLMS14} managed to bypass
the browser-based {\sc xss} filters of the
73\% of 1,602 real-world {\sc dom}-based {\sc xss} vulnerabilities.
These vulnerabilities were actually found during
their previous research~\cite{LSJ13}.
Furthermore, in the publications that
{\sc amnesia}~\cite{HO05,HO06,HO05b}
and {\sc sd}river~\cite{MS09,MKS09,MKLS11} were presented,
authors managed to break existing application suites
and then test the diagnostic performance of their tools on them.

% Comment: The above are some extra findings that
% indicate that there is no standard way to
% test such mechanisms. Perhaps, forming a
% standard way to test such tools in terms
% of diagnostic and computational performance
% would be one of the reasons of adopting them.

Consider the majority of mechanisms coming from
the policy enforcement category. In most cases
developers should modify multiple components
to use each mechanism. Specifically, mechanisms like
BrowserShield, and {\sc beep} require modifications
both on the server and the client side.
Thus, it would be difficult for them to be adopted by
both browser vendors and application developers.
